Railway: Adaptive Disk Storage for Interaction Graphs

### 2014-09-19 docs/edbt2015/text/optimal.tex
the first cut of the ILP formulation is completed

\subsection{Storage Overhead Formulation}
\noindent
The storage overhead is defined as the additional amount of disk space used to
store the sub-blocks, normalized by the original space needed by a single
block (no partitioning). The storage overhead can be formalized as follows,
for the non-overlapping case:
\begin{equation}
H(\mathcal{P}, B) = (|\mathcal{P}(B)|-1)\cdot\Big(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\Big)
\label{eq:nov}
\end{equation}

Basically, for the non-overlapping case, there is no overhead due to the
attributes, as they are not repeated. However, there is overhead for the block
structure that is repeated for each sub-block. There are $|\mathcal{P}(B)|-1$
such extra sub-blocks, and for each, the contribution to the overhead due to
storing the graph structure is given by $s(B)-c_e(B)\cdot \sum_{a\in A} s(a)$.
Equation~\ref{eq:nov} has one nice feature, that is, it does not depend on the
details of the attribute partitioning, other than the number of partitions. We
make use of this feature, later for the ILP formulation of the problem.

>>>>

\subsection{Storage Overhead Formulation}
\noindent
The storage overhead is defined as the additional amount of disk space used to
store the sub-blocks, normalized by the original space needed by a single
block (no partitioning). The storage overhead can be formalized as follows,
for the non-overlapping case:
\begin{equation}
H(\mathcal{P}, B) = (|\mathcal{P}(B)|-1)\cdot\Big(1-\frac{c_e(B)\cdot \sum_{a\in A} s(a)}{s(B)}\Big)
\label{eq:nov-ohead}
\end{equation}

Basically, for the non-overlapping case, there is no overhead due to the
attributes, as they are not repeated. However, there is overhead for the block
structure that is repeated for each sub-block. There are $|\mathcal{P}(B)|-1$
such extra sub-blocks, and for each, the contribution to the overhead due to
storing the graph structure is given by $s(B)-c_e(B)\cdot \sum_{a\in A} s(a)$.
Eq.~\ref{eq:nov-ohead} has one nice feature, that is, it does not depend on the
details of the attribute partitioning, other than the number of partitions. We
make use of this feature, later for the ILP formulation of the problem.
